### 2015-05-05 internal_review_response.Rnw

Page 10: A section on package dependencies might be a good addition.

{\it I've added a footnote that directs readers to the package index page on CRAN where the dependencies and package imports can be viewed.  I'm not sure it's worth describing each in detail since this is readily available in the source code.}

Page 10: Include an example of this in the code examples below.

{\it The example for \texttt{aggregswmp} was modified to show this issue.}

@@

Page 10: rewrite. ``a signal from noisy data'' ??

Page 12, line 262: Omit.

{\it The sentence was revised to remove the following: `...with arguments passed to the \texttt{filter} function from the R base installation'.}

@@

Page 13: or

{\it Changed.}

Page 14: May not be obvious that this is 60 min / 15 min... And character string options are a great idea!

{\it Text was modified for clarity: `...96 if the time step is 15 minutes (24 hours * 60 minutes / 15 minutes).  The frequency of a parameter with annual periodicity at a 15 minute time step would be 35040 (365 days * 24 hours * 60 minutes / 15 minutes).'}

@@

Page 16: I'm just being picky, but the name on this one is tripping me up. I think I'd prefer to see eco\_metab. But, I realize that may not be an easy change, so up to you!

{\it I'm trying to reduce the number of underscores in the function names so I've kept \texttt{ecometab}.}

Page 14, line 310: Omit `respectively'.

@@

{\it Omitted.}

Page 17: Do all of these functions need to be exported? Could they simply be internal functions that the users don't see? If so, you could shorten or eliminate this section. Also you could create a Viz category of functions instead of this one. In that you could talk about the plot capabilites separate from the analysis section, and the include the reserve\_map function there.

{\it I'm hesitant to change the Namespace of the package too much because I don't want to break any functions that depend on the exported functions in the miscellaneous category.  I've also exported a lot of these functions because some users might be interested in seeing the source code, such as for the \texttt{calckl} function used by \texttt{ecometab}.  That being said, I have shortened the section to emphasize these points and have moved the \texttt{map\_reserve} function to the previous section.  I suppose looking at site locations could be considered `analysis' if you are using spatial location to interpret trends.}

@@

Page 19: Yank this. Goes without saying.

{\it Removed.}

Page 20: Some of the figures have code that directly preceeds it. Other figures (like Fig 8) it is a bit more difficult to link code to figure. Would be nice to provide a link to code for all the figures. This way a reader could download a single script to reproduce the figures.

{\it I've added an R script to the supporting information that reproduces the figures/tables in the manuscript.}

### 2015-05-05 swmpr_manu.Rnw
almost done with internal revisions, upload tangled script for reproducing figures/tables

latex(
  to_tab[, 'Description', drop = F],
  file = '',
  caption = 'Retrieval functions available from the SWMPr package. Full documentation for each function is in the help file (e.g., execute \\texttt{?all\\_params} at the command line).',
  rowlabel = 'Function',
  colheads = 'Description',
  rowname = to_tab$Functions,
  caption.loc = 'top',
  col.just=c("p{3.5in}"), 
  label = 'tab:retrieve', 
  table.env = FALSE
  )
@

@@

to_tab <- data.frame(Attributes = atts, Class = atts_class, Description = atts_desc, stringsAsFactors = F)
foot <- c('\\textsuperscript{\\textit{a}}\\footnotesize Time zones that do not observe daylight savings are used for \\texttt{swmpr} objects and may not be cities in the United States.  For example, ``America/Jamaica" is the same as Eastern Standard Time.')

@@

latex(
  to_tab[, -1, drop = F],
  file = '',
  caption = "Attributes of a \\texttt{swmpr} object that describe characteristics of the data.  Similar information can be obtained using the \\texttt{str} function.",
  rowlabel = 'Attributes',
  colheads = c('Class', 'Description'),
  rowname = to_tab$Attributes,
  caption.loc = 'top',
  insert.bottom = foot,
  col.just=c("p{0.75in}", "p{3.25in}"), 
  label = 'tab:attributes', 
  table.env = FALSE
  )
@

@@

latex(
  to_tab[, 'Description', drop = F],
  file = '',
  caption = "Organizing functions available from the SWMPr package. Full documentation for each function is in the help file (e.g., execute \\texttt{?comb} at the command line).",
  rowlabel = 'Function',
  colheads = 'Description',
  rowname = to_tab$Functions,
  caption.loc = 'top',
  col.just=c("p{3.5in}"), 
  label = 'tab:organize', 
  table.env = FALSE
  )
@

@@

The \texttt{comb} function is used to combine multiple \texttt{swmpr} objects into a single object with a continuous time series at a given step.  The \texttt{timestep} function is used internally such that \texttt{timestep} and \texttt{differ} are accepted arguments for \texttt{comb}.  All arguments must be called explicitly since an arbitrary number of \texttt{swmpr} objects can be used as input.  The function combines data by creating a master time series that is used to iteratively merge all \texttt{swmpr} objects.  The time series for merging depends on the value passed to the \texttt{method} argument.  Passing \texttt{`union'} to \texttt{method} will create a time series that is continuous from the earliest and latest dates for all input objects.  Passing \texttt{`intersect`} to \texttt{method} will create a time series that is continuous from the set of dates that are shared between all input objects.  Finally, a seven or eight character station name passed to \texttt{method} will merge all data based on a continuous time series for the specified station, which must be present in the input data.  Currently, combining identical data types from different stations is not possible (e.g., two water quality stations from the same reserve).

@@

The \texttt{aggreswmp} function aggregates parameter data for a \texttt{swmpr} object by set units of time.  This function is most useful for aggregating noisy data to evaluate trends on longer time scales or to simply reduce the size of a dataset.  Data can be aggregated by years, quarters, months, weeks, days, or hours by a predefined function, which defaults to the mean.  A \texttt{swmpr} object is returned for the aggregated data, although the \texttt{datetimestamp} vector will be converted to a date object if the aggregation period is a day or longer.  Days are assigned to the date vector if the aggregation period is a week or longer based on the \texttt{round} method for IDate objects created in the data.table package \cite{Dowle14}.  Additionally, the method of treating \texttt{NA} values for the aggregation function should be noted since this may greatly affect the quantity of data that are returned, particularly for nutrient data.

@@

funcs <- c('aggreswmp', 'aggremetab', 'ecometab', 'decomp', 'decomp\\_cj', 'hist', 'lines', 'na.approx', 'plot', 'plot\\_metab', 'plot\\_summary', 'smoother')
funcs <- paste0('\\texttt{', funcs, '}')

descrips <- c(
  'Aggregate \\texttt{swmpr} objects for different time periods - years, quarters, months,  weeks, days, or hours.  The aggregation function defaults to the mean.',
  'Aggregate metabolism data from a \\texttt{swmpr} object.  This is primarly used within \\texttt{plot\\_metab} but may be useful for simple summaries of raw metabolism data.',
  'Estimate ecosystem metabolism for a combined water quality and weather dataset using the open-water method.',
  'Decompose a \\texttt{swmpr} time series into trend, seasonal, and residual components.  This is a simple wrapper to \\texttt{decompose} \\cite{Kendall83}.  Decomposition of monthly or daily trends is possible.',
  'Decompose a \\texttt{swmpr} time series into grandmean, annual, seasonal, and events components.  This is a simple wrapper to \\texttt{decompTs} in the wq package \\cite{Jassby14}.  Only monthly decomposition is possible.',
  'Plot a histogram for a \\texttt{swmpr} object.',
  'Add lines to an existing plot created with \\texttt{plot}.',
  'Linearly interpolate missing data (\\texttt{NA} values) in a \\texttt{swmpr} object. The maximum gap size that is interpolated is defined by the arguments.', 
  'Plot a univariate  time series for a \\texttt{swmpr} object.  The parameter name must be specified.',
  'Plot ecosystem metabolism estimates after running \\texttt{ecometab} on a \\texttt{swmpr} object.',  
  'Create summary plots of seasonal/annual trends and anomalies for a water a single paramter of interest.',
  'Smooth \\texttt{swmpr} objects with a moving window average.  Window size and sides (e.g., centered) can be specified, passed to \\texttt{filter}.'
  )

@@

latex(
  to_tab[, 'Description', drop = F],
  file = '',
  caption = "Analysis functions available from the SWMPr package.  Full documentation for each function is in the help file (e.g., execute \\texttt{?aggreswmp} at the command line).",
  rowlabel = 'Function',
  colheads = 'Description',
  rowname = to_tab$Functions,
  caption.loc = 'top',
  col.just=c("p{3.5in}"), 
  label = 'tab:analyze', 
  table.env = FALSE
  )
@

<<eval = F, cache = T>>=
# get data
data(apacpwq)
dat <- qaqc(apacpwq)

# get mean DO by months
aggreswmp(dat, 'months', params = c('do_mgl'))
@

Time series can be smoothed to better characterize a signal independent of noise (\Cref{fig:smooth_ex}).  Although there are many approaches to smoothing, a moving window average is intuitive and commonly used.  The \texttt{smoother} function can be used to smooth parameters in a \texttt{swmpr} object using a specified window size with arguments passed to the \texttt{filter} function from the base installation.  The \texttt{window} argument specifies the number of observations included in the moving average where larger windows result in greater smoothing.  The \texttt{sides} argument specifies how the average is calculated for each observation.  Setting \texttt{sides = 1} will filter observations within the window that are previous to the current observation, whereas \texttt{sides = 2} will filter observations within the window centered at zero lag from the current observation. As before, the \texttt{params} argument specifies which parameters to smooth.

@@

The disaggregation of time series into additive of multiplicative components that can be attributed to separate sources of variance is another common application for trend analysis.  The \texttt{decomp} function is a simple wrapper to \texttt{decompose} \cite{Kendall83} that separates a time series into components describing a trend, cyclical variation (e.g., daily or annual), and the remainder  (\Cref{fig:decomp_ex1}).  An additive decomposition assumes that the cyclical component of the time series is stationary (i.e., the variance is constant), otherwise a multiplicative decomposition can be used.  The \texttt{frequency} argument describes the periodicity of the cyclical parameter in units of the native time step.  For example, the \texttt{frequency} for a parameter with daily periodicity would be 96 if the time step is 15 minutes (4 * 24).  The frequency of a parameter with annual periodicity at a 15 minute time step would be 35040 (4 * 24 * 365).  For simplicity, character strings of \texttt{`daily'} or \texttt{`annual'} can be supplied in place of numeric values, although any number can be used to identify an arbitrary cyclical component.  A starting value of the time series must be supplied in the latter case that indicates the sequence in the cycle for the first observation (e.g., 1 if the the first observation is at sunrise for a diurnal cycle).\footnote{The value is passed to the \texttt{ts} function, \url{https://stat.ethz.ch/R-manual/R-devel/library/stats/html/ts.html}}  Use of the \texttt{setstep} function is also required to standardize the time step prior to decomposition.

@@

An alternative approach to time series decomposition is provided by the \texttt{decomp\_cj} function, which is a simple wrapper to the \texttt{decompTs} function in the wq package \cite{Cloern10,Jassby14}.  The \texttt{decomp\_cj} function provides only a monthly decomposition, which is appropriate for characterizing relatively long-term trends.  This approach works best for nutrient data that are typically obtained on a monthly cycle.  The function will also work with continuous water quality or weather data but note that the data must first be aggregated on the monthly scale before decomposition.  Additionally, the time series is decomposed into the grandmean, annual, seasonal, and events components, as compared to trend, seasonal, and random components for the \texttt{decomp} function described above.  For both, the random or events components, respectively, can be considered anomalies that do not follow the trends in the remaining categories.  Additional arguments passed to \texttt{decompTs} can be used with \texttt{decomp\_cj}, such as \texttt{startyr}, \texttt{endyr}, and \texttt{type}.  Values passed to \texttt{type} are \texttt{mult} (default) or \texttt{add}, referring to multiplicative or additive decomposition.  \Cref{fig:decomp_ex2} shows the results from the \texttt{decomp\_cj} function applied to a multi-year chlorophyll time series.

@@

@@

funcs <- c('calckl', 'map\\_reserve', 'metab\\_day', 'param\\_names', 'parser', 'swmpr', 'time\\_vec')
funcs <- paste0('\\texttt{', funcs, '}')

descrips <- c(
  'Estimate the reaeration coefficient for air-sea gas exchange.  Used in the \\texttt{ecometab} function.',
  'Create a map of all stations in a reserve using the ggmap package.',
  'Identify the metabolic day for each approximate 24 period in an hourly time series.  Used in the \\texttt{ecometab} function.',
  'Returns column names as a list for the parameter types (nutrients, weather, or water quality).  Includes \\ac{QAQC} columns with \\texttt{f\\_} prefix. Used in the data retrieval functions.',
  'Parses HTML returned from \\ac{CDMO} data requests.  Used in the retrieval functions.',
  'Creates a \\texttt{swmpr} object class.  Used in the data retrieval functions.',
  'Converts time vectors to \\texttt{POSIXct} objects with the appropriate time zone for a site.  Used in the data retrieval functions.'
  )

@@

For brevity, only the \texttt{reserve\_map} function is discussed.  This function can be used to create a map with all stations at a reserve using functions in the ggmap package \cite{Kahle13}. The current function is limited to Google maps of four types that can be set with the \texttt{map\_type} argument: terrain (default), satellite, roadmap, or hybrid.  The \texttt{zoom} argument may have to be chosen through trial and error depending on the spatial extent of the reserve.  See the help documentation for the \texttt{ggmap} function for more info on \texttt{zoom}.

@@

The ability to evaluate environmental characteristics between estuaries within the \ac{NERRS} program has been greatly improved using functions in the SWMPr package.  This section describes three examples using the SWMPr package to illustrate the improved ability to synthesize and evaluate multi-year time series of estuarine data. First, the open-water method for estimating metabolism was applied to nearly all co-located water quality and weather sites at each \ac{NERRS} reserve using all years of available data.  The results are provided primarily to illustrate ease of use of the functions and secondarily to provide an update on metabolism estimates using the most recent \ac{SWMP} data.  Caffrey \cite{Caffrey03} and Caffrey \cite{Caffrey04} applied the open-water method to estimate ecosystem metabolism using five years of water quality observations at two sites at each of the \ac{NERRS} reserves.  The air-sea gas exchange model also assumed a constant value for the reaeration coefficient, whereas the current \texttt{ecometab} function provides a more accurate estimate by including weather data in the calculation (see Caffrey et al. \cite{Caffrey14} for details).

@@

>>>>

latex(
  to_tab[, 'Description', drop = F],
  file = '',
  caption = "Retrieval functions available from the SWMPr package. Full documentation for each function is in the help file (e.g., execute \\texttt{?all\\_params} for individual functions or \\texttt{help.search(`retrieve', package = `SWMPr')} for all).",
  rowlabel = 'Function',
  colheads = 'Description',
  rowname = to_tab$Functions,
  caption.loc = 'top',
  col.just=c("p{3.5in}"), 
  label = 'tab:retrieve', 
  table.env = FALSE
  )
@

@@

to_tab <- data.frame(Attributes = atts, Class = atts_class, Description = atts_desc, stringsAsFactors = F)
foot <- c('\\textsuperscript{\\textit{a}}\\footnotesize Time zones that do not observe daylight savings are used for \\texttt{swmpr} objects and may not be cities in the United States.  For example, ``America/Jamaica" is used for Eastern Standard Time.')

@@

latex(
  to_tab[, -1, drop = F],
  file = '',
  caption = "Attributes of a \\texttt{swmpr} object that describe characteristics of the data.",
  rowlabel = 'Attributes',
  colheads = c('Class', 'Description'),
  rowname = to_tab$Attributes,
  caption.loc = 'top',
  insert.bottom = foot,
  col.just=c("p{0.75in}", "p{3.25in}"), 
  label = 'tab:attributes', 
  table.env = FALSE
  )
@

@@

latex(
  to_tab[, 'Description', drop = F],
  file = '',
  caption = "Organizing functions available from the SWMPr package. Full documentation for each function is in the help file (e.g., execute \\texttt{?comb} for individual functions or \\texttt{help.search(`organize', package = `SWMPr')} for all).",
  rowlabel = 'Function',
  colheads = 'Description',
  rowname = to_tab$Functions,
  caption.loc = 'top',
  col.just=c("p{3.5in}"), 
  label = 'tab:organize', 
  table.env = FALSE
  )
@

@@

The \texttt{comb} function is used to combine multiple \texttt{swmpr} objects into a single object with a continuous time series at a given step.  The \texttt{timestep} function is used internally such that \texttt{timestep} and \texttt{differ} are accepted arguments for \texttt{comb}.  All arguments must be called explicitly since an arbitrary number of \texttt{swmpr} objects can be used as input.  The function combines data by creating a master time series that is used to iteratively merge all \texttt{swmpr} objects.  The time series for merging depends on the value passed to the \texttt{method} argument.  Passing \texttt{`union'} to \texttt{method} will create a time series that is continuous from the earliest and latest dates for all input objects.  Passing \texttt{`intersect'} to \texttt{method} will create a time series that is continuous from the set of dates that are shared between all input objects.  Finally, a seven or eight character station name passed to \texttt{method} will merge all data based on a continuous time series for the specified station, which must be present in the input data.  Currently, combining identical data types from different stations is not possible (e.g., two water quality stations from the same reserve).

@@

The \texttt{aggreswmp} function aggregates parameter data for a \texttt{swmpr} object by set units of time.  This function is most useful for aggregating noisy data to evaluate trends on longer time scales or to simply reduce the size of a dataset.  Data can be aggregated by years, quarters, months, weeks, days, or hours by a predefined function, which defaults to the mean.  A \texttt{swmpr} object is returned for the aggregated data, although the \texttt{datetimestamp} vector will be converted to a date object if the aggregation period is a day or longer.  Days are assigned to the date vector if the aggregation period is a week or longer based on the \texttt{round} method for IDate objects created in the data.table package \cite{Dowle14}.  Additionally, the method of treating \texttt{NA} values for the aggregation function should be noted since this may greatly affect the quantity of data that are returned, particularly for nutrient data (see the example below).

@@

funcs <- c('aggreswmp', 'aggremetab', 'ecometab', 'decomp', 'decomp\\_cj', 'hist', 'lines', 'map\\_reserve', 'na.approx', 'plot', 'plot\\_metab', 'plot\\_summary', 'smoother')
funcs <- paste0('\\texttt{', funcs, '}')

descrips <- c(
  'Aggregate \\texttt{swmpr} objects for different time periods - years, quarters, months,  weeks, days, or hours.  The aggregation function defaults to the mean.',
  'Aggregate metabolism data from a \\texttt{swmpr} object.  This is primarly used within \\texttt{plot\\_metab} but may be useful for simple summaries of raw metabolism data.',
  'Estimate ecosystem metabolism for a combined water quality and weather dataset using the open-water method.',
  'Decompose a \\texttt{swmpr} time series into trend, seasonal, and residual components.  This is a simple wrapper to \\texttt{decompose} \\cite{Kendall83}.  Decomposition of monthly or daily trends is possible.',
  'Decompose a \\texttt{swmpr} time series into grandmean, annual, seasonal, and events components.  This is a simple wrapper to \\texttt{decompTs} in the wq package \\cite{Jassby14}.  Only monthly decomposition is possible.',
  'Plot a histogram for a \\texttt{swmpr} object.',
  'Add lines to an existing plot created with \\texttt{plot}.',
  'Create a map of all stations in a reserve using the ggmap package.',
  'Linearly interpolate missing data (\\texttt{NA} values) in a \\texttt{swmpr} object. The maximum gap size that is interpolated is defined by the arguments.', 
  'Plot a univariate  time series for a \\texttt{swmpr} object.  The parameter name must be specified.',
  'Plot ecosystem metabolism estimates after running \\texttt{ecometab} on a \\texttt{swmpr} object.',  
  'Create summary plots of seasonal/annual trends and anomalies for a water a single paramter of interest.',
  'Smooth \\texttt{swmpr} objects with a moving window average.  Window size and sides (e.g., centered) can be specified, passed to \\texttt{filter}.'
  )

@@

latex(
  to_tab[, 'Description', drop = F],
  file = '',
  caption = "Analysis functions available from the SWMPr package.  Full documentation for each function is in the help file (e.g., execute \\texttt{?aggreswmp} for individual functions or \\texttt{help.search(`analyze', package = `SWMPr')} for all).",
  rowlabel = 'Function',
  colheads = 'Description',
  rowname = to_tab$Functions,
  caption.loc = 'top',
  col.just=c("p{3.5in}"), 
  label = 'tab:analyze', 
  table.env = FALSE
  )
@

<<eval = T, cache = T>>=
# get data, keep all observations
data(apacpnut)
dat <- qaqc(apacpnut, qaqc_keep = NULL)

# aggregate by quarters
agg_dat <- aggreswmp(dat, by = 'quarters')
nrow(agg_dat)

# aggregate by quarters, remove rows with NA values
# note the reduction in the number of rows
agg_dat2 <- aggreswmp(dat, by = 'quarters', na.action = na.omit)
nrow(agg_dat2)
@

Time series can be smoothed to better characterize a signal from noisy data (\Cref{fig:smooth_ex}).  Although there are many approaches to smoothing, a moving window average is intuitive and commonly used.  The \texttt{smoother} function can be used to smooth parameters in a \texttt{swmpr} object using a specified window size.  The \texttt{window} argument specifies the number of observations included in the moving average where larger windows result in greater smoothing.  The \texttt{sides} argument specifies how the average is calculated for each observation.  Setting \texttt{sides = 1} will filter observations within the window that are previous to the current observation, whereas \texttt{sides = 2} will filter observations within the window centered at zero lag from the current observation. As before, the \texttt{params} argument specifies which parameters to smooth.

@@

The disaggregation of time series into additive or multiplicative components that can be attributed to separate sources of variance is another common application for trend analysis.  The \texttt{decomp} function is a simple wrapper to \texttt{decompose} \cite{Kendall83} that separates a time series into components describing a trend, cyclical variation (e.g., daily or annual), and the remainder  (\Cref{fig:decomp_ex1}).  An additive decomposition assumes that the cyclical component of the time series is stationary (i.e., the variance is constant), otherwise a multiplicative decomposition can be used.  The \texttt{frequency} argument describes the periodicity of the cyclical parameter in units of the native time step.  For example, the \texttt{frequency} for a parameter with daily periodicity would be 96 if the time step is 15 minutes (24 hours * 60 minutes / 15 minutes).  The frequency of a parameter with annual periodicity at a 15 minute time step would be 35040 (365 days * 24 hours * 60 minutes / 15 minutes).  For simplicity, character strings of \texttt{`daily'} or \texttt{`annual'} can be supplied in place of numeric values, although any number can be used to identify an arbitrary cyclical component.  A starting value of the time series must be supplied in the latter case that indicates the sequence in the cycle for the first observation (e.g., 1 if the the first observation is at sunrise for a diurnal cycle).\footnote{The value is passed to the \texttt{ts} function, \url{https://stat.ethz.ch/R-manual/R-devel/library/stats/html/ts.html}}  Use of the \texttt{setstep} function is also required to standardize the time step prior to decomposition.

@@

An alternative approach to time series decomposition is provided by the \texttt{decomp\_cj} function, which is a simple wrapper to the \texttt{decompTs} function in the wq package \cite{Cloern10,Jassby14}.  The \texttt{decomp\_cj} function provides only a monthly decomposition, which is appropriate for characterizing relatively long-term trends.  This approach works best for nutrient data that are typically obtained on a monthly cycle.  The function will also work with continuous water quality or weather data but note that the data must first be aggregated on the monthly scale before decomposition.  Additionally, the time series is decomposed into the grandmean, annual, seasonal, and events components, as compared to trend, seasonal, and random components for the \texttt{decomp} function described above.  For both, the random or events components can be considered anomalies that do not follow the trends in the remaining categories.  Additional arguments passed to \texttt{decompTs} can be used with \texttt{decomp\_cj}, such as \texttt{startyr}, \texttt{endyr}, and \texttt{type}.  Values passed to \texttt{type} are \texttt{mult} (default) or \texttt{add}, referring to multiplicative or additive decomposition.  \Cref{fig:decomp_ex2} shows the results from the \texttt{decomp\_cj} function applied to a multi-year chlorophyll time series.

@@

Finally, the \texttt{map\_reserve} function can be used to create a map with all stations at a reserve using functions in the ggmap package \cite{Kahle13}. This map may be useful for aiding the interpretation of spatial trends in water quality parameters given the relative locations in a reserve.  The current function is limited to Google maps of four types that can be set with the \texttt{map\_type} argument: terrain (default), satellite, roadmap, or hybrid.  The \texttt{zoom} argument can be chosen through trial and error depending on the spatial extent of the reserve.  See the help documentation for the \texttt{ggmap} function for more info on \texttt{zoom}.

@@

funcs <- c('calckl', 'metab\\_day', 'param\\_names', 'parser', 'swmpr', 'time\\_vec')
funcs <- paste0('\\texttt{', funcs, '}')

descrips <- c(
  'Estimate the reaeration coefficient for air-sea gas exchange.  Used in the \\texttt{ecometab} function.',
  'Identify the metabolic day for each approximate 24 period in an hourly time series.  Used in the \\texttt{ecometab} function.',
  'Returns column names as a list for the parameter types (nutrients, weather, or water quality).  Includes \\ac{QAQC} columns with \\texttt{f\\_} prefix. Used in the data retrieval functions.',
  'Parses HTML returned from \\ac{CDMO} data requests.  Used in the retrieval functions.',
  'Creates a \\texttt{swmpr} object class.  Used in the data retrieval functions.',
  'Converts time vectors to \\texttt{POSIXct} objects with the appropriate time zone for a site.  Used in the data retrieval functions.'
  )

@@

@@

This section describes three examples using the SWMPr package to illustrate the improved ability to synthesize and evaluate multi-year time series of estuarine data. First, the open-water method for estimating metabolism was applied to nearly all co-located water quality and weather sites at each \ac{NERRS} reserve using all years of available data.  The results are provided primarily to illustrate ease of use of the functions and secondarily to provide an update on metabolism estimates using the most recent \ac{SWMP} data.  Caffrey \cite{Caffrey03} and Caffrey \cite{Caffrey04} applied the open-water method to estimate ecosystem metabolism using five years of water quality observations at two sites at each of the \ac{NERRS} reserves.  The air-sea gas exchange model also assumed a constant value for the reaeration coefficient, whereas the current \texttt{ecometab} function provides a more accurate estimate by including weather data in the calculation (see Caffrey et al. \cite{Caffrey14} for details).

@@

\subsection*{Source code for reproducing figures/tables}

Source code as an R script for reproducing figures and tables in the manuscript: \href{}{}
